Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-06 Latex Source/paper.tex
add typing results, conclusion, and abstract

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass[sigconf]{acmart}

% part of the template 
\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

% packages that I added
\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}
\usepackage[section]{placeins} %% used to keep the images in the section that I want them in

@@

\begin{abstract}
The abstract does not get added until after the project is finished or nearly finished.
\end{abstract}

@@

\section{Related Works}
\subsection{Music While Working}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. 
The other studies attempted to search for this answer by focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. 
Similar to Kiss and Linnell~\cite{kiss2021effect}, Mathew ~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. 
A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. 
According to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality. 
Furnham et al., also determined this was based on personality in a study done between extraverts and introverts although ``no significant interactions were found''~\cite{distractingEffectsFurnham}.

@@

\subsection{Eye Tracking and Quantified Behavioral Test}

CITATIONS ABOUT EYE TRACKING AND QBTEST HERE

\section{Methodology}
\subsection[short]{Equipment} 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest. 
Participants used the MacBook Pro with the eye tracker for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. 
A bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
the space bar on the MacBook.
Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{typingTest}
  \caption{Images of what the user will see in the typing test}
  \Description{Images of what the user will see in the typing test}
  \label{typingTest}
\end{figure}

After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure~\ref*{typingTest}a. The participants saw Figure~\ref*{typingTest}b while the test was running, while Figure~\ref*{typingTest}c was the signifier that the typing portion was finished.

@@

\begin{figure}
  \center
  \includegraphics[width=0.4\textwidth]{eyetracker_setup.png}
  \caption{EyeWriter 2.0 Setup}
  \Description{Image of the eye tracker setup}
  \label{EyeWriter}
\end{figure}

Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study. 
The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration. This can be seen in Figure~\ref*{EyeWriter}.

Participants were seated in a comfortable position facing the laptop screen.
The laptop is placed on top of a laptop stand while the eye tracker is mounted on a wooden frame. 
While the eye tracker is on a moveable slider, it is centered in front of the screen. 
At the ends of the wooden frame are infrared lights that flash at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).

\begin{figure}
  \includegraphics[width=\textwidth]{qbTest.png}
  \caption{Images of what the user will see in the QBTest}
  \Description{Images of what the user will see in the QBTest}
  \label{QBTest}
\end{figure}

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
The user will then see Figure~\ref*{QBTest}. Figure~\ref*{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
Figure~\ref*{QBTest}b is what the user will see during the test. Figure~\ref*{QBTest}b also displays what the user will see when they are correct and incorrect.
Figure~\ref*{QBTest}c displays for only two minutes but shows the user their score.
% MAYBE ADD MORE ABOUT THE QBTEST?

\section{Results and Discussion}
Within-subjects testing was used for our ten participants. Individually the typing test and QBTest scores were not statistically significant, whereas 
% WHATEVER TYPE OF TESTING IS USED (ANOVA)
the ANOVA from the heatmap with the eyetracker, the results were statistically significant. %sounds clunky might change
The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
dependent variables. 
While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
The bar graph for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
lyrical music and instrumental music.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{time}
  \caption{Time (s) of participants for typing test}
  \Description{Bar graph for participants in seconds}
  \label{time}
\end{figure}

\section{Conclusion and Future Works}
Conclusion

>>>>

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass[sigconf]{acmart}
% part of the template 
\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

% packages that I added
\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}
% \usepackage[section]{placeins} %% used to keep the images in the section that I want them in

@@

\begin{abstract}
A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
a type of eye tracker, will track the participants eye movements.
Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
% add results from two tests together
\end{abstract}

@@

\section{Related Works}
\subsection{Music While Working}  % if we don't add anything to \subsection{Eye Tracking and Quantified Behavioral Test} we need to remove this subsection
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. 
The other studies attempted to search for this answer by focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. 
Similar to Kiss and Linnell~\cite{kiss2021effect}, Mathew ~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. 
A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. 
According to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality. 
Furnham et al., also determined this was based on personality in a study done between extraverts and introverts although ``no significant interactions were found''~\cite{distractingEffectsFurnham}.

@@

\subsection{Eye Tracking and Quantified Behavioral Test}
% if we don't add anything here we can remove this subsection before we submit

% CITATIONS ABOUT EYE TRACKING AND QBTEST HERE

\section{Methodology}
\subsection[short]{Equipment} 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest. 
Participants used the MacBook Pro with the eye tracker for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. 
A Bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
the space bar on the MacBook.
Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{typingTest}
  \caption{Images of what the user will see in the typing test}
  \Description{Images of what the user will see in the typing test}
  \label{typingTest}
\end{figure}

After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure~\ref{typingTest}a. The participants saw Figure~\ref{typingTest}b while the test was running, while Figure~\ref{typingTest}c was the signifier that the typing portion was finished.

@@

\begin{figure}
  \center
  \includegraphics[width=0.5\textwidth]{eyetracker_setup.png}
  \caption{EyeWriter 2.0 Setup}
  \Description{Image of the eye tracker setup}
  \label{EyeWriter}
\end{figure}

Following the typing test, participants proceeded to the cognitive task component of the study, which was also conducted under the three aforementioned conditions. 
While the participants did the cognitive task of a quantified behavioral test, their eye movement will be tracked by the EyeWriter 2.0 camera that we specially built for this study. 
The EyeWriter 2.0 system consists of a camera mounted on the participant's laptop, which tracks eye movements and allows for precise measurement of gaze direction and fixation duration. This can be seen in Figure~\ref{EyeWriter}.

Participants were seated in a comfortable position facing the laptop screen.
The laptop is placed on top of a laptop stand while the eye tracker is mounted on a wooden frame. 
While the eye tracker is on a moveable slider, it is centered in front of the screen. 
At the ends of the wooden frame are infrared lights that flash at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
Although not pictured, a Bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).

\begin{figure}
  \includegraphics[width=0.5\textwidth]{qbTest.png}
  \caption{Images of what the user will see in the QBTest}
  \Description{Images of what the user will see in the QBTest}
  \label{QBTest}
\end{figure}

During the cognitive task component of the study, participants performed a Quantified Behavioral test or QBTest while their eye movements were tracked by the EyeWriter 2.0.
The QBTest is a computerized test designed to assess various aspects of cognitive function, including attention, impulsivity, and response control.
The user will then see Figure~\ref{QBTest}. Figure~\ref{QBTest}a is the screen that will be displayed before the participant is ready to begin the QBTest.
Figure~\ref{QBTest}b is what the user will see during the test. Figure~\ref{QBTest}b also displays what the user will see when they are correct and incorrect.
Figure~\ref{QBTest}c displays for only two minutes but shows the user their score.
% MAYBE ADD MORE ABOUT THE QBTEST?

\section{Results and Discussion}
Within-subjects testing was used for our ten participants. Individually the typing test and QBTest scores were not statistically significant, whereas 
% WHATEVER TYPE OF TESTING IS USED (ANOVA)
the ANOVA from the heatmap with the eyetracker, the results were statistically significant. %sounds clunky might change
The ANOVA for the typing test was done twice for the dependent variables, time and accuracy, as GoStats did not allow for multiple 
dependent variables. The accuracy for all participants were not necessarily an indicator of good results as all the participants were 
allowed to use the backspace to re-try any letters that were mis-typed.

\begin{figure}
  \includegraphics[width=0.3\textwidth]{time}
  \caption{Time (s) of participants for typing test}
  \Description{Bar graph for participants in seconds}
  \label{timeL}
\end{figure}

While not statistically significant, the \textit{p} value for time was 0.1172 whereas the \textit{p} value for accuracy was 0.2334.
The bar graph in Figure~\ref{timeL} for time in seconds for the typing test was quite telling. The condition for no music was consistently faster than both
lyrical music and instrumental music. The typing tests unfortuntely did not record which typing test of the five that each participant did so we
were unable to compare each test against another participant with the same test.

\section{Conclusion and Future Works}
% Don't forget to add results to the abstract as we cannot finsih until everything is done for the rest of the paper.
While the typing test was not statistically significant, there were at least two factors that should be changed should someone else recreate this study or 
further expand. The typing test should record which typing test a participant does. While the ones included are similar in length and difficulty, some 
participants said that some were easier becuase they recognized the lyrics from the songs used in the typing test and that they found the ones they 
recognized easier and faster for them to type. Although time may be a constraint, more text should be added to the typing test. It is not necessarily 
known if recognizable songs were a factor but older songs or different text completely could be implemented.
